sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2018-03-16 inst/documents/rotations_notes.Rmd
notes

@@

~ in run_rot finish code condensing around :
      raf_m <- RAF[insecticide, 'm', 'intervention',gen-1]
      raf_f <- RAF[insecticide, 'f', 'intervention',gen-1]

@@

~ Maybe don't allow coverage to be set to 0 ? or put in some kind of warning.

~ can I create an easy function to compare two scenarios (seq & rotate) with otherwise same params ?

>>>>

*16/3/18*
~ code condensing in run_rot()

~ added stop in run_rot() for if coverage=0

~ looking at comparing two scenarios (rot & seq) on same plot

I tried this before with : df_resanother in rot_plots. It puts on the resistance curves for the 2 scenarios, but doesn't show the insecticide use for each
dfseq <- run_rot(n_insecticides=2, rot_interval=0, expo_hi=0.5, eff=0.5, cost=0.01, coverage=1)
dfrot <- run_rot(n_insecticides=2, rot_interval=15, expo_hi=0.5, eff=0.5, cost=0.01, coverage=1)
rot_plot_resistance(dfrot, df_resanother=dfseq, plot_refuge=FALSE)

dfseq <- run_rot(rot_interval=0, max_gen = 300, migration=0.01, expo_hi=0.8, eff=0.8, cost=0.1, coverage=1)
dfrot <- run_rot(rot_interval=6, max_gen = 300, migration=0.01, expo_hi=0.8, eff=0.8, cost=0.1, coverage=1)
rot_plot_resistance(dfrot, df_resanother=dfseq, plot_refuge=FALSE)

I have improved plotting of 2 scenarios together.
Seems that overshooting problem occurs in rotations. Possibly because rotations are not stopped when the threshold is reached. See dfrot from prev e.g. whichj keeps going up to 0.62 at gen 127. This may not matter if the counting of gens only includes those < 0.5. The other option is to stop rotations early,m which I thought I was already doing with exit_rot = TRUE ??

in insecticide_check() exit_rot should prompt exit from rotation when 0.5 threshold is exceeded.

dfrot2 <- run_rot(rot_interval=6, max_gen = 300, migration=0.01, expo_hi=0.8, eff=0.8, cost=0.1, coverage=1, diagnostics=TRUE)

Aha! It could be a problem with min_rwr_interval, which is 5 by default and so may force staying within rotations and thus cause overshooting of threshold.

But i thought that only gens under thresh are counted ???

@@

~ check how gens_under_thresh are counted in sensi_an_rotations1
    summarise(gens_dep_under50 = sum(resistance < 0.5 &
                                     #finds insecticide in use = this one
                                     resist_gene==paste0('insecticide',insecticide), na.rm=TRUE)) %>%
                                 summarise(tot_gens_dep_under50 = sum(gens_dep_under50)) %>%    
                                 unlist()

~ move github repo back to mine
~~ From Github I merged changes from Ians with a pull request after comparing across the forks.
~~ Now I can possibly change RStudio to point to the repo on my Github (do when I have a bit more time)
~~ update R

@@
